\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage[pdftex,bookmarks=true,bookmarksnumbered=true,pdfauthor={Urs Reupke},pdftitle={Anathema Installation Guide}]{hyperref}
\usepackage[pdftex]{graphics}
\usepackage{graphicx}
\usepackage{textcomp}

\title{Anathema Installation Guide\\ Target Program Version: 0.8\footnote{Some features might not be available in prior versions.}}
\author{Anathema created by Sandra Sieroux and Urs Reupke\\ with contributions by Daniel Hohenberger and the Exalted community}
\date{}

\begin{document}
\sffamily
\maketitle
\tableofcontents
\bigskip
The installation procedure for Anathema has remained almost constant since our second release in January 2004. Many a question was asked and answered since then. To the benefit of future users, I have tried to compile the knowledge gained since then into a single document. 

I hope for this guide to answer all question that arise during download, installation and configuration of Anathema. All you require are a standard issue PC, internet access and basic computer skills.

I have tried to keep the guide independent of operating system specialties - and I failed spectacularly. If anything does not work as written or needs further clarification for a specific system, please let me know. This is especially true of Mac OS X, which I have never even touched. A plethora of contact options is provided at the Anathema website\footnote{http://anathema.sf.net}. You can also mail me directly\footnote{urskr@users.sf.net}.
\begin{flushright}
Enjoy Anathema\\
	-Urs
\end{flushright}
\include{SecsSetup}
\begin{appendix}
\section*{Revisions}
\begin{description}
\item[08/15/05] - Added ``doc'' folder to list of package contents. (\ref{sub:PackageContents})\newline
Added ``per-user'' comment to preferences introduction. (\ref{sec:Preferences})
\item[08/14/05] - Initial Release
\end{description}
\end{appendix}
\end{document}